\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-24 paper.qmd

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = b, 
                         y = log(MSE))) + 
  geom_point(
    size = 0.6
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  geom_vline(xintercept = 264, linetype="solid", 
             color = "black", linewidth=0.5, alpha = 0.5) +
  ylab("log(MSE)") +
  xlab("b") +
  ggtitle("(a)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, 
            angle=90),
        title = element_text(size = 36))
```

@@

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = benchmark_rm_lwd, 
                         y = log(MSE))) + 
  geom_point(
    size = 0.6
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  geom_vline(xintercept = benchmark1, linetype="solid", 
             color = "black", linewidth=0.5, alpha = 0.5) +
  scale_x_continuous("standardized bin count", 
         transform = "reverse") + 
  ylab("log(MSE)") +
  ggtitle("(c)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, 
            angle=90),
        title = element_text(size = 36))
```

@@

#| label: fig-dist-scurve
#| out-width: 100%
#| fig-width: 8
#| fig-height: 6
#| fig-pos: H

>>>>

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = b, 
                         y = log(MSE))) + 
  geom_point(size = 1) +
  geom_line() + 
  geom_vline(xintercept = 190, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  geom_vline(xintercept = 91, linetype=2, 
             color = "black", linewidth=0.8, alpha = 0.5) +
  geom_vline(xintercept = 364, linetype=2, 
             color = "black", linewidth=0.8, alpha = 0.5) +
  ylab("log(MSE)") +
  xlab("b") +
  ggtitle("(a)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, 
            angle=90),
        title = element_text(size = 72))
```

@@

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = benchmark_rm_lwd, 
                         y = log(MSE))) + 
  geom_point(
    size = 0.6
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  geom_vline(xintercept = benchmark1, linetype="solid", 
             color = "black", linewidth=0.5, alpha = 0.5) +
  scale_x_continuous("standardized bin count", 
         transform = "reverse") + 
  ylab("log(MSE)") +
  ggtitle("(c)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, 
            angle=90),
        title = element_text(size = 72))
```

@@

#| label: fig-dist-scurve
#| out-width: 100%
#| fig-width: 12
#| fig-height: 10
#| fig-pos: H

### 2024-06-24 paper.tex

\caption{\label{fig-bins-scurve}Hexbin plots from different number of
bins for the UMAP applied to S-curve data: (a) \(b = 91\) (7, 13), (b)
\(b = 264\) (12, 22), and (c) \(b = 364\) (14, 26). The hexbins are
colored based on the density of points, with darker colors indicating
higher density and yellow color representing lower density within each
bin. What is the number of bins that would be effective?}

>>>>

\caption{\label{fig-bins-scurve}Hexbin density plots of UMAP layout of
the S-curve data, using three different bin inputs: (a) \(b = 91\) (7,
13), (b) \(b = 190\) (10, 19), and (c) \(b = 364\) (14, 26). Color
indicates standardized counts, dark indicating high count and light
indicates low count. At the smallest bin size the data segregates into
two separate groups, suggesting this is too many bins. Using the MSE of
the model fit in \(p-D\) helps decide on a useful choice of number of
bins.}
